---
title: "Transport Data"
output: html_notebook
---
## 1. Installing and Using the Packages

Before Starting Coding, Clean all datas in the memory .
library() specifies that packages to be used.
Installing and using Required Packages for the Project:
  Go to the Bottom right side where from the 5 tabs Click the Packages Tab and Click Install in the first line and type the 4 packages name inside seperated by space or ,


```{r}
# install.packages("ggplot2")  # Add # before code after 1st Run
library(ggplot2)
# install.packages("dplyr")  # Add # before code after 1st Run
library(dplyr)
# install.packages("sqldf")  # Add # before code after 1st Run
library(sqldf)
# install.packages("tidyr")  # Add # before code after 1st Run
library(tidyr)
# install.packages("scales")  # Add # before code after 1st Run
library(scales)
library('rpart')
```
Reading the CSV Files: \
1) Getting the Current Directory \
2) Setting the Working Directory (Replace \ by \\ or /)  \
3) Checking the file exists or not \
4) Reading ot Uploading the CSV file into the R \
```{r}
getwd()
setwd("C:/Users/spiro/Documents/Projects/")
file.exists("ITBD10.csv")
Trans <- read.csv("ITBD10.csv",TRUE,stringsAsFactors = FALSE)
```
Viewing the Data
```{r}
View(Trans)
```
##Understandinng the Data
1) Structure of the Data
```{r}
str(Trans)
```
2) First 6 Data to Understand the table
```{r}
head(Trans,10)
```
3) Dimensions of the Data:
```{r}
dim(Trans)
```
4) Column names of the Data:
```{r}
colnames(Trans)
```
## Cleaning the Data:

Checking for NA
```{r}
is.na(Trans)
```
Any Na Data's in Dataset
```{r}
any(is.na(Trans))
```
Summarizing the Data
```{r}
summary(Trans)
```

```{r}
trans1 <- Trans [,c(1,5:15)]
```
#Visualization of Data:
```{r}
ggplot(trans1, aes(PROBLEM, fill=REVIEW )) + geom_bar() +
  ggtitle("How Much Complaints have been Recorded") +
  theme(axis.text.x = element_text(angle = 65, hjust = 1)) +
  ylab("Complaints")
```
How much Records (Travels) from different source:
```{r}
ggplot(trans1, aes(FROM,  mean(RATING), fill=REVIEW )) + geom_bar(stat = "identity") +
  ggtitle("Count of Source (FROM)") +
  theme(axis.text.x = element_text(angle = 65, hjust = 1)) +
  ylab("RATINGS")
```

```{r}
ggplot(trans1, aes(DESTINATION_PLACE, RATING, fill=REVIEW )) + geom_bar(stat = "identity") +
  ggtitle("Destination") +
  theme(axis.text.x = element_text(angle = 65, hjust = 1)) +
  ylab("Ratings")
```

```{r}
ggplot(trans1, aes(TYPE, RATING, fill=REVIEW )) + geom_bar(stat = "identity") +
  ggtitle("TYPE OF VEHICLE USED") +
  theme(axis.text.x = element_text(angle = 65, hjust = 1)) +
  ylab("TRIPS Went")
```



## Checking for the Most Popular Tourist
```{r}
trans_f <- trans1 %>% select(FROM, RATING) %>% group_by(FROM) %>% 
  summarise(mr = mean(RATING) )
trans_f <- trans_f %>% arrange(desc(mr))
trans_f
```
##Tourist Places with the Highest Number of Ratings
```{r}
trans_d <- trans1 %>% select(DESTINATION_PLACE, RATING) %>% group_by(DESTINATION_PLACE) %>% summarise(mr = mean(RATING))
trans_d <- trans_d %>% arrange(desc(mr))
trans_d
```
